Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
move text to the motivation section

The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling.

Between May 2011 and May 2014, the CVE database~\cite{cve-database} lists
83 vulnerabilities when searching for the string ``ZIP''. Of these, 42
were completely unrelated to the archive format, for example reporting
vulnerabilities revealing ZIP codes of other users. 26 vulnerabilities
were related to ZIP archives, but not to input processing, such as
trusting arbitrary update ZIP files sent to a server or vulnerabilities
that can be accessed through manipulating files in a ZIP container. This
includes several vulnerabilities allowing another files to replaced while
they are extracted from ZIP files because insufficiently secure temporary
directories are used. Of the 15 remaining vulnerabilities pertaining
to ZIP files, 14 vulnerabilities were related to input processing. The
other vulnerability, which falls outside of Nail's purview, concerns a
ZIP packer choosing a weak legacy cryptosystem even when configured to
use AES.

Nail parsers are immune by design to vulnerabilities like these 14.
Ten of those vulnerabilities are memory corruption attacks, that could
also be avoided by using safer languages.  Most of the buffer overflows
seem to result from inconsistent offset fields being manipulated
without checking.  Because Nail's generated code checks offsets before
reading and does not expose any untrusted pointers to the application,
it protects against memory corruption attacks by design.

The remaining four vulnerabilities do not involve memory corruption,
but rather parser ambiguities.  Two of them relate to implementations
mis-parsing ZIP files, particularly in virus scanners. One other
vulnerability is in a Python ZIP library, which uses both the size
field in the file entry and in the header, without checking for their
consistency.  This results in a denial-of-service through endless loops
or incorrectly extracted ZIP files.

A similar attack was used by the fourth vulnerability, the infamous
Android master key bug~\cite{saurik-masterkey} that completely
bypassed Android security through parser inconsistencies between the
ZIP handler that checks signatures for privileged applications and the
ZIP implementations that ultimately extract those files. Thus, valid
application bundles could be modified to include malicious applications
without breaking their signatures. Instead of both components containing
an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

>>>>

XXX refer back to \S\ref{s:motivation}.

Nail parsers are immune by design to vulnerabilities like these 14.
Because Nail's generated code checks offsets before reading and does not
expose any untrusted pointers to the application, it protects against
memory corruption attacks by design.

Nail also protects against parser ambiguity vulnerabilities.

Instead of both components containing
an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

### 2014-05-01 paper/osdi14/motivation.tex
move text to the motivation section

@@

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) was used to reject over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.

>>>>

To motivate the need for Nail, this section presents a case study of
vulnerabilities due to ad-hoc input parsing and output generation.

The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling.
\XXX[what is the PROTOS Genome project?]

Between May 2011 and May 2014, the CVE database~\cite{cve-database} lists
83 vulnerabilities when searching for the string ``ZIP''. Of these, 42
were completely unrelated to the archive format, for example reporting
vulnerabilities revealing ZIP codes of other users. 26 vulnerabilities
were related to ZIP archives, but not to input processing, such as
trusting arbitrary update ZIP files sent to a server or vulnerabilities
that can be accessed through manipulating files in a ZIP container. This
includes several vulnerabilities allowing another files to replaced while
they are extracted from ZIP files because insufficiently secure temporary
directories are used. Of the 15 remaining vulnerabilities pertaining
to ZIP files, 14 vulnerabilities were related to input processing. The
other vulnerability, which falls outside of Nail's purview, concerns a
ZIP packer choosing a weak legacy cryptosystem even when configured to
use AES.

Out of the 14 input processing vulnerabilities, ten are memory corruption
attacks, that could also be avoided by using safer languages.  Most of
the buffer overflows seem to result from inconsistent offset fields
being manipulated without checking.

The remaining four vulnerabilities do not involve memory corruption,
but rather parser ambiguities.  Two of them relate to implementations
mis-parsing ZIP files, particularly in virus scanners.  One other
vulnerability is in a Python ZIP library, which uses both the size
field in the file entry and in the header, without checking for their
consistency.  This results in a denial-of-service through endless loops
or incorrectly extracted ZIP files.

A similar attack was used by the fourth vulnerability, the infamous
Android master key bug~\cite{saurik-masterkey} that completely
bypassed Android security through parser inconsistencies between the
ZIP handler that checks signatures for privileged applications and the
ZIP implementations that ultimately extract those files. Thus, valid
application bundles could be modified to include malicious applications
without breaking their signatures.

@@

% Proper input recognition has been shown to be an excellent way of
% eliminating ambiguous inputs.  In one case, a PDF parser (implemented
% in Coq) was used to reject over $95\%$ of known malicious PDFs by checking
% whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
% also produced a ``counter-example'' PDF that triggered numerous bugs
% in other PDF parsers. However, manually writing parser code and proving
% unambiguity does not scale to the number of file formats and protocols
% in existence and might result in parser code tied to one specific
% application. By supporting a wide range of real-world file formats,
% Nail helps programmers produce precise parsers for complex grammars.
